\LARGE \bf A Formal Description of Bitcoin's Script Language

### 2017-03-20 paper.tex
Removed red instructions from the paper

\textcolor{red}{\textit{To describe and motivate the problem or your survey topic }}\\

@@

\textcolor{red}{\textit{Detailed description of the approach, and highlight the main technical difficulties and novelties. }}\\

@@

$\bullet$ \texttt{OP\_CHECKSIG} is a bitch to describe.

@@

\textcolor{red}{\textit{Detailed discussion of related work. Should stress how these relate to your work. Simply list and describe what other people did is not sufficient.}}\\

@@

\textcolor{red}{\textit{Again summarize the work and discuss possible future work.}}\\

>>>>

@@

@@

%$\bullet$ \texttt{OP\_CHECKSIG} is a bitch to describe.

@@

@@
